\enableregime[utf]  % use UTF-8

\setupcolors[state=start]
\setupinteraction[state=start, color=middleblue] % needed for hyperlinks

\setuppapersize[letter][letter]  % use letter paper
\setuplayout[width=middle, backspace=1.5in, cutspace=1.5in,
             height=middle, header=0.75in, footer=0.75in] % page layout
\setuppagenumbering[location={footer,center}]  % number pages
\setupbodyfont[11pt]  % 11pt font
\setupwhitespace[medium]  % inter-paragraph spacing

\setuphead[section][style=\tfc]
\setuphead[subsection][style=\tfb]
\setuphead[subsubsection][style=\bf]

% define title block commands
\unprotect
\def\doctitle#1{\gdef\@title{#1}}
\def\author#1{\gdef\@author{#1}}
\def\date#1{\gdef\@date{#1}}
\date{\currentdate}  % Default to today unless specified otherwise.
\def\maketitle{%
  \startalignment[center]
    \blank[2*big]
      {\tfd \@title}
    \blank[3*medium]
      {\tfa \@author}
    \blank[2*medium]
      {\tfa \@date}
    \blank[3*medium]
  \stopalignment}
\protect

% define descr (for definition lists)
\definedescription[descr][
  headstyle=bold,style=normal,align=left,location=hanging,
  width=broad,margin=1cm]

% prevent orphaned list intros
\setupitemize[autointro]

% define defaults for bulleted lists 
\setupitemize[1][symbol=1][indentnext=no]
\setupitemize[2][symbol=2][indentnext=no]
\setupitemize[3][symbol=3][indentnext=no]
\setupitemize[4][symbol=4][indentnext=no]

\setupthinrules[width=15em]  % width of horizontal rules

% for block quotations
\unprotect

\startvariables all
blockquote: blockquote
\stopvariables

\definedelimitedtext
[\v!blockquote][\v!quotation]

\setupdelimitedtext
[\v!blockquote]
[\c!left=,
\c!right=,
before={\blank[medium]},
after={\blank[medium]},
]

\protect

\doctitle{Philosophy 463: Second Assignment}
\author{David Sanson}
\date{February 23, 2010}
\starttext
\maketitle

\startitemize
\item
  Answer one of the following prompts in no more than 1300 words.
\item
  Your paper should be double-spaced with 1" margins and 12 pt serif
  font.
\item
  Include a word count with your paper.
\item
  Cite all sources.
\item
  This is not a research paper: your task is to analyze what you have
  read, not to go off and read other stuff.
\item
  Due in class {\bf Wednesday, March 10th}.
\stopitemize

\subsubject{Prompts}

\startitemize[n][stopper=.]
\item
  The Resemblance Nominalist tries to reduce talk of properties to
  talk of resemblance classes. How does that reduction go? What is
  Russell's objection to the reduction? What is Price's response? Who
  is right?
\item
  Armstrong argues that there are no uninstantiated universals. What
  is the issue that uninstantiated universals pose for the Immanent
  Realist? What are Armstrong's arguments against uninstantiated
  universals? Are they compelling?
\stopitemize

\stoptext

